---
title: "Practical Machine Learning Project"
output: html_document
---
###Summary  
  
Measurements were collected for users performing various exercises while wearing a motion-sensoring device. Using these data, an algorithm was created to predict if the user had performed the exercise correctly or incorrectly (4 types of errors).

###Load the Data  
  
Load the data sets (training and problem set) while removing the various error characters.
```{r}
trainorig<-read.csv("training.csv", header=TRUE, na.strings=c("#DIV/0!","","NA","NULL"))
problem<-read.csv("testing.csv", header=TRUE, na.strings=c("#DIV/0!","","NA","NULL"))
```
  
###Data Processing  
  
Separate the training data into a training and testing set for cross validation purposes:

```{r}
library(caret)
intrain<-createDataPartition(y=trainorig$classe, p=.6, list=FALSE)
train<-trainorig[intrain,]
test<-trainorig[-intrain,]
```
  
Remove columns where all data is "NA"  
```{r}
train<-train[colnames(train[colSums(is.na(train))==0])]
test<-test[colnames(test[colSums(is.na(test))==0])]
```
  
Remove the columns 1-7 which are not predictor variables. Generate a prediction model using Random Forests
```{r}
train2<-train[,-c(1:7,60)]
train2$classe<-train$classe
library(randomForest)
modfit<-randomForest(classe~., train2)
```
  
Use the model to predict the class of the exercises in the test set. 
```{r}
test2<-test[,-c(1:7,60)]
predict<-predict(modfit, newdata=test2)
```
View the model to receive an output of the error estimate.
Create a confusion matrix to see how accurate the model predicted the test set.
```{r}
modfit
confusionMatrix(predict,test$classe)
```
See from the confusion matrix that the predictions were very close and accuracy is high. An estimate for the out-of-sample error is seen above (about 0.6%).  
The model was used to predict the classe factor for the problem set with a 20/20 accuracy.
